---
title: "remote_r_test"
author: "Sam Bogan"
date: "2025-02-11"
output: html_document
---
What to do before running the R code below

1. Install macFUSE and sshfs

2. Create local working directory to mount to your remote directory

3. In Github, create a new repo named remote_r_test

4. Create a new version-controlled R project on your local device and associate it with the new repo

5. Create a remote working directory as a destination for the repo on hb

6. Transfer the .Rproj file and metadata to your new working directory on hb

7. Mount using sshfs 

```{bash}

## For macos
# Use homebrew for macFUSE
brew install macFUSE

# Install sshf at https://macfuse.github.io/

# Create your local working directory
mkdir ~/Documents/remote_r_test

# Mount with sshfs
sshfs snbogan@hb.ucsc.edu:/hb/home/snbogan/remote_r_test/ ~/Documents/remote_r_test

```

Run R code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
library(tidyverse)

```

```{r}

# Create and write some data
test_df <- data.frame(var = c(1.1, 1.83, 3.067, 3.91),
                      val = c(1,2,3,4))

write.csv(test_df, "test.csv", row.names = FALSE)

# Plot your fake data to show it in-line in the RMD
ggplot(data = test_df,
       aes(x = var, y = val)) +
  geom_smooth(method = "lm") +
  geom_point(size = 3) +
  theme_classic(base_size = 15)

```

