---
title: "remote_r_test"
author: "Sam Bogan"
date: "2025-02-11"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(root = "/hb/home/snbogan/remote_r_test/")

```

What to do before running the R code below

1. Install macFUSE and sshfs

2. Create local working directory to mount to your remote directory

3. In Github, create a new repo named remote_r_test

4. Create a new version-controlled R project on your local device and associate it with the new repo

5. Create a remote working directory as a destination for the repo on hb

6. Transfer the .Rproj file and metadata to your new working directory on hb

7. Mount using sshfs 

## bash commands for your local machine

```{bash}

## For macos
# Use homebrew for macFUSE
brew install macFUSE

# Install sshf at https://macfuse.github.io/

# Create your local working directory
mkdir ~/Documents/remote_r_test

# Mount with sshfs
sshfs snbogan@hb.ucsc.edu:/hb/home/snbogan/remote_r_test/ ~/Documents/remote_r_test

```

```{r}

# Create mock data in working directory
df <- data.frame(x = c("I", "am", "Sam"),
                 y = c("Sam", "I", "am"))

# Export mock data to csv
write.csv(df, file = "test.csv", row.names = FALSE)

```


# Start an interactive session and R in terminal: send commands to terminal

```{bash}

## Send to terminal

# Log in to hb
ssh snbogan@hb.ucsc.edu

# Start interactive session
salloc --account=pi-jkoc --partition=lab-colibri --qos=pi-jkoc --ntasks=1 --cpus-per-task=4 --mem=16G --time=04:00:00

# Check node allocation
hostname

# Load and start R
module load r

R

```

## Run R code in through terminal

```{r}

# Load packages
library(tidyverse)
library(MASS)

# Move to working directory
setwd('/hb/home/snbogan/remote_r_test')

## Send to console

# Set seed for reproducibility
set.seed(123)

# Define the number of observations
n <- 100000

# Define the mean and standard deviation for the two variables
mean_X <- 50
sd_X <- 10
mean_Y <- 30
sd_Y <- 5

# Define the correlation coefficient
rho <- 0.7  # Adjust as needed

# Create the covariance matrix
cov_matrix <- matrix(c(sd_X^2, rho * sd_X * sd_Y, 
                       rho * sd_X * sd_Y, sd_Y^2), 
                     nrow = 2)

# Simulate the data
sim_data <- mvrnorm(n, mu = c(mean_X, mean_Y), Sigma = cov_matrix)

# Convert to a data frame
df2 <- data.frame(X = sim_data[, 1], Y = sim_data[, 2])

# Plot your fake data to show it in-line in the RMD
fig <- ggplot(data = df,
       aes(x = X, y = Y)) +
  geom_point(size = 1, alpha = .25) +
  theme_classic(base_size = 15)

write.csv(df2, "test2.csv", row.names = FALSE)

save(fig, file = "fig.Rdata")

```

Run R commands on local console

```{r}

# Read in and print the datasheet
test_df <- read.csv("test.csv")

test_df

# Load and print your fig.Rdata
load("fig.Rdata")

# Print the loaded fig
fig

```


